---
title: "R_and_Python_ML_workflow"
description: |
  Taking the `radix` R package for a test spin with `Scikit Learn`!
author:
  - name: Ashish Dutt 
    url: https://duttashi.github.io/blog
    affiliation: Universiti Malaya
    affiliation_url: www.fsktm.um.edu.my
date: "2018-10-08"
output: radix::radix_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,      # Output code chunks
    message = FALSE,  # Toggle off message output 
    warning = FALSE)  # Toggle off warning output
```

```{r}
# Reference website
# https://www.business-science.io/business/2018/10/08/python-and-r.html#part1
```

```{r}
library(reticulate)
```

```{r}
# R
conda_list()
```

```{r}
# R tell reticulate to use miniconda3
use_condaenv("miniconda3")
```
#### Machine Learning with Scikit Learn

```{python}
import numpy as np
import pandas as pd
from sklearn.model_selection import train_test_split
from sklearn import preprocessing
from sklearn.ensemble import RandomForestRegressor
from sklearn.pipeline import make_pipeline
from sklearn.model_selection import GridSearchCV
from sklearn.metrics import mean_squared_error, r2_score
from sklearn.externals import joblib
```
Next, import the data using read_csv() from pandas. Note that the separator is a semicolon (not a comma which is what most data sets are stored as in CSV format). The data is stored as a Python object named data
```{python}
# Python
dataset_url = 'http://mlr.cs.umass.edu/ml/machine-learning-databases/wine-quality/winequality-red.csv'
data = pd.read_csv(dataset_url, sep = ";")
```

We can use the print() function to output Python objects.
```{python}
print(data.head())
```

Note, any attempt to use R functions on the `data` object will yield some jargon! Why is it so, because, the object was created using `python function`. To perform, R related operations, ensure the data is read as an `R object`.

```{r}
head(data)
tail(data)
```
```{r}
library(data.table)
```

```{r}
mydat<- fread('http://mlr.cs.umass.edu/ml/machine-learning-databases/wine-quality/winequality-red.csv')
```

```{r}
head(mydat)
tail(mydat)
```

